\Huge \scshape \fontfamily{pbk}\fontsize{50}{40}\selectfont The Dark \LaTeX{} \\ \medskip \normalfont \medskip\Huge An Example of the dndbook Class

### 2024-10-30 example.tex

\usepackage[utf8]{inputenc}
\usepackage[singlelinecheck=false]{caption}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{shortvrb}
\usepackage{stfloats}
\usetikzlibrary{intersections} % Required for ornamentedtabular

@@

@@

    \DndMonsterDetails[
        %saving-throws = {Str +0, Dex +0, Con +0, Int +0, Wis +0, Cha +0},
        %skills = {Acrobatics +0, Animal Handling +0, Arcana +0, Athletics +0, Deception +0, History +0, Insight +0, Intimidation +0, Investigation +0, Medicine +0, Nature +0, Perception +0, Performance +0, Persuasion +0, Religion +0, Sleight of Hand +0, Stealth +0, Survival +0},
        %damage-vulnerabilities = {cold},
        %damage-resistances = {bludgeoning, piercing, and slashing from nonmagical attacks},
        %damage-immunities = {poison},
        %condition-immunities = {poisoned},
        senses = {darkvision 60 ft., passive Perception 10},
        languages = {Common, Goblin, Undercommon},
        challenge = 1,
        proficiency = +2,
      ]
    % Traits
    \DndMonsterAction{Innate Spellcasting}
    Foo's spellcasting ability is Charisma (spell save DC 12, +4 to hit with spell attacks). It can innately cast the following spells, requiring no material components:
    \begin{DndMonsterSpells}
      \DndInnateSpellLevel{misty step}
      \DndInnateSpellLevel[3]{fog cloud, rope trick}
      \DndInnateSpellLevel[1]{identify}
    \end{DndMonsterSpells}

@@

The stat block can be formatted either as a single column, or as a block that spans the page horizontally.

>>>>

\usepackage[utf8]{inputenc}
\usepackage[singlelinecheck=false]{caption}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{shortvrb}
\usepackage{stfloats}
\usetikzlibrary{intersections} % Required for ornamentedtabular
\usepackage{wrapfig}

@@

You can represent an attached note (for example, for notes from Bigby or Mordenkainen) using the |DndAside| environment.

\begin{DndAside}
  This is the part where I give you a little extra information or make a witty comment to keep you entertained while you read.
\end{DndAside}

The |DndQuotation| environment goes a little further, offering the option of comment attribution, and tilts the note at a slight angle.

\begin{DndQuotation}{The Author}
  This is the part where I give you a little extra information or make a witty comment to keep you entertained while you read.
\end{DndQuotation}

@@

    \DndMonsterDetails[
        %saving-throws = {Str +0, Dex +0, Con +0, Int +0, Wis +0, Cha +0},
        %skills = {Acrobatics +0, Animal Handling +0, Arcana +0, Athletics +0, Deception +0, History +0, Insight +0, Intimidation +0, Investigation +0, Medicine +0, Nature +0, Perception +0, Performance +0, Persuasion +0, Religion +0, Sleight of Hand +0, Stealth +0, Survival +0},
        %damage-vulnerabilities = {cold},
        %damage-resistances = {bludgeoning, piercing, and slashing from nonmagical attacks},
        %damage-immunities = {poison},
        %condition-immunities = {poisoned},
        senses = {darkvision 60 ft., passive Perception 10},
        languages = {Common, Goblin, Undercommon},
        challenge = 1,
        proficiency = +2,
      ]

    \DndMonsterAction{Innate Spellcasting}
    Foo's spellcasting ability is Charisma (spell save DC 12, +4 to hit with spell attacks). It can innately cast the following spells, requiring no material components:
    \begin{DndMonsterSpells}
      \DndInnateSpellLevel{misty step}
      \DndInnateSpellLevel[3]{fog cloud, rope trick}
      \DndInnateSpellLevel[1]{identify}
    \end{DndMonsterSpells}

@@

When used with the |stats=modern| package option, some additional values are available for customization: |DndMonsterBasics| takes an |initiative| option to display as part of the initial block; it appears to the right of the \textbf{Armor Class} option. The |DndMonsterAbilityScores| command now has options for |str save|, |dex save|, etc, which if provided will replace the values in the appropriate \textbf{save} column of the abilities block. Lastly, modern stat blocks use an explicit section title for traits (the actions appearing between |DndMonsterDetails| and the \textbf{Actions} section). WotC also seems to have moved most \textbf{Spellcasting} blocks into the \textbf{Actions} section, though whether you also do this is a matter of personal style.

%% Manually toggle a bunch of internals to produce a modern stat block as an example.
%% This will happen automatically if you use the |stats=modern| package option.

\ExplSyntaxOn
\let\DndMonster\DndMonsterModernBg
\let\endDndMonster\endDndMonsterModernBg
\bool_set_true:N \l__dnd_modern_stats_bool
\ExplSyntaxOff

    % If you want to use commas in the key values, enclose the values in braces.
    \DndMonsterBasics[
        armor-class = {9 (12 with \emph{mage armor})},
        hit-points  = {\DndDice{3d8 + 3}},
        speed       = {30 ft., fly 30 ft.},
        initiative  = --1,
      ]

    \DndMonsterDetails[
        %saving-throws = {Str +0, Dex +0, Con +0, Int +0, Wis +0, Cha +0},
        %skills = {Acrobatics +0, Animal Handling +0, Arcana +0, Athletics +0, Deception +0, History +0, Insight +0, Intimidation +0, Investigation +0, Medicine +0, Nature +0, Perception +0, Performance +0, Persuasion +0, Religion +0, Sleight of Hand +0, Stealth +0, Survival +0},
        %damage-vulnerabilities = {cold},
        %damage-resistances = {bludgeoning, piercing, and slashing from nonmagical attacks},
        %damage-immunities = {poison},
        %condition-immunities = {poisoned},
        senses = {darkvision 60 ft., passive Perception 10},
        languages = {Common, Goblin, Undercommon},
        challenge = 1,
      ]

    \DndMonsterSection{Traits}
    \DndMonsterAction{Innate Spellcasting}
    Foo's spellcasting ability is Charisma (spell save DC 12, +4 to hit with spell attacks). It can innately cast the following spells, requiring no material components:
    \begin{DndMonsterSpells}
      \DndInnateSpellLevel{misty step}
      \DndInnateSpellLevel[3]{fog cloud, rope trick}
      \DndInnateSpellLevel[1]{identify}
    \end{DndMonsterSpells}

\ExplSyntaxOn
\bool_set_false:N \l__dnd_modern_stats_bool
\let\DndMonster\DndMonsterClassicBg
\let\endDndMonster\endDndMonsterClassicBg
\ExplSyntaxOff
